\begin{document}

\chapter{Introduction}
\section{Computational-historical Analysis of Semantic Change}
Language is constantly changing and evolving. The emergence of new senses, the demise of old ones, and the polysemous nature of linguistic expressions make the process of semantic change a dynamic phenomenon \parencite{robertinvanhove2008}. As individuals learn new words and meanings throughout their life, so does a language. As language users actively engage in processing and interpreting the language, the semantic history of words are woven into the texts that then survive time and are presented to us now. In the long run, a word is likely to convey a meaning completely different or unfathomable. For instance, ``the quick and the dead'', quoted from the Bible, means ``the living and the dead'', but the collective adjective ``the quick'' no longer makes sense in Present-Day English \parencite[199]{semanticincrowley2010}.

The nature of language is reflected in its use. In \citeyear{sinclair1982reflections}, \citeauthor{sinclair1982reflections} envisions the possibility of ``vast, slowing changing stores of text'' and ``detailed evidence of language evolution'' \ascitedin{renouf2002time}. In recent years, a huge volume of historical textual data have been digitalized and made available to the public, and the use of digital libraries as rich linguistic resources to observe how certain linguistic features are accepted and/or ``assimilated'' into the language becomes more and more feasible \parencite{renouf2002time}. While recent studies have used time-sliced collections of texts to observe swift meaning changes, the digitalization of texts from earlier time periods opens up research opportunities that incorporates a corpus-driven approach to trace the diachronic development of words and their meanings \parencite{kutuzov2018survey,tahmasebi2018survey,camacho2018survey,hamilton2016cultural,jawahar2019contextualized}.

With the recent advances in Natural Language Processing (NLP) techniques, the changes in meaning over time can to a great extent be captured by representing discrete linguistic data as numeric vectors such as word embeddings, especially after the release of Word2vec \parencite{mikolov2013efficient}, GloVe \parencite{pennington2014glove} and FastText \parencite{bojanowski2016enriching}. For instance, regarding the study of semantic change of individual words across time, initial efforts have been put into generating word embeddings from different time spans to explore whether semantic change occurs based on the neighboring words of the target word from each time period.

As a pioneering computational-historical investigation in Mandarin, the monosyllabic word \zh{家}{jiā}{home} is selected as a case study in this thesis. The concept of home is an ancient, seemingly familiar and encompassing, but tangible one. Various humanities disciplines have sought to grasp the full picture. Defined by the Oxford English Dictionary (OED), the word \textit{home} is ``the place where a person or animal dwells'' \dictcite{homeinoed}. As one of the earliest 1\% entries to be included in the OED, this word has \num{35} main senses and \num{214} total senses--Home is a physical space, a place where we feel a ``sense of belonging [and] comfort'', and even a person's ``country or native land.'' In Mandarin Chinese, the MOE Revised Mandarin Chinese Dictionary defines its translated equivalent 家 \textit{jiā} as ``a place where family members live together (眷屬共同生活的場所)'', ``a private property (私有財產)'', and ``people in certain professional fields (經營某種行業或具有某種身份的人)'' \dictcite{jiainmoe}. Yet, how is the concept of home encoded linguistically? Specifically, how its diachrony interacts with synchrony and variations is the main concern of this study.

\section{Research Questions}
From the perspective of corpus-based computational linguistics, research questions are invoked as to how the concept of home is properly computationally represented? What words are semantically related to this concept? How are these words co-construct the meanings of home, and how this concept comes into shape through the lens of time. The research questions are to be answered through a corpus-based case study approach along with diachronic word embeddings to investigate the evolution of meaning change in the target word \jia\rspace. In this study, the research questions are proposed as follows:

\begin{enumerate}[label={(\arabic*)},nolistsep]
    \item How can diachronic embeddings be applied to textual data of pre-modern Chinese?
    \item Besides the linguistic factor of frequency change, how is semantic change of \jia be reflected in distributional ways?
    \item What cultural implications can diachronic embeddings contribute to pre-modern Chinese?
\end{enumerate}
% \vspace*{\baselineskip}

\section{Organization of the Study}
The remainder of this thesis is organized as follows. A theoretical overview and reflections of lexical semantic change in general, the concept of home in literature, as well as the diachronic embeddings techniques are given in Chapter~\ref{related_works}. Chapter~\ref{methods} introduces the collected textual data and the preprocessing issues, along with the proposed corpus-based clustering method and distributed semantic representation models for the study. The development of word-level and sense-level word representations brings to the fine-grained analyses and generalizations of semantic change. Chapter~\ref{results} describes how the proposed approaches are evaluated, and showcases analyses made possible by our approach, and discusses the gained insights and limitations. Finally, Chapter~\ref{conclusions} concludes with a summary of the contributions and considerations on the future works as well as on its usefulness to linguistic investigations and other social-cultural applications.

\end{document}